Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-18 manuscript/ERL_global_C_review.Rmd
added stacked age trends figures to manuscript
#58

# DISPLAY ITEMS
#figures
schematic =1
figure_map=2
diagram_TrB_mature= 3
diagram_TeB_mature=4
diagram_TeN_mature=5
diagram_BoN_mature=6
all_diagrams_mature="3-6"
flux_age_trends=7
stock_age_trends=8

#tables
variables_table=1

@@

### Biome differences
Forest C cycling varies enormously across biomes...
Biome is an artificial categorical distinction convenient for categorizing the world's forests according to major differences in climate and vegetation.

The most important gradient for defining biomes is climate. 
Since (Humboldt?), it has been recognized that climate plays a dominant role in shaping differences among forests.

@lieth_primary_1973 synthesized differences in NPP across gradients of mean annual temperature and precipitation.

@@

>>>>

# DISPLAY ITEMS
#tables
variables_table=1

#figures
schematic =1
figure_map=2
diagram_TrB_mature= 3
diagram_TeB_mature=4
diagram_TeN_mature=5
diagram_BoN_mature=6
all_diagrams_mature="3-6"
flux_age_trends=7
stock_age_trends=8
TrB_age_trends=9

age_trends_caption_generic= "Selection of variables for plotting seeks to maximize sample size and broad geographic representation while representing all elements of C cycle. Asterisks indicate variables whose age trends were calculated based on other variables, as follows: $R_{auto}=NPP $ ,$B_{ag-wood}=B_{ag}-B_{foliage}$, $B_{root-coarse}=B_{root}-B_{root-fine}$."
TrB_age_trends_caption = paste("Figure 9 | Age trends in C cycling in tropical broadleaf forests.", age_trends_caption_generic) 
TeB_age_trends_caption = paste("Figure 10 | Age trends in C cycling in temperate broadleaf forests.", age_trends_caption_generic) 
TeN_age_trends_caption = paste("Figure 11 | Age trends in C cycling in temperate conifer forests.", age_trends_caption_generic) 
BoN_age_trends_caption = paste("Figure 12 | Age trends in C cycling in boreal conifer forests.", age_trends_caption_generic)

@@

### Biome differences

Forest C cycling varies enormously across biomes, which are artificial categorical distinctions convenient for categorizing the world's forests according to major differences in climate, vegetation, *etc.* 
Since *(Humboldt?)*, it has been recognized that climate plays a dominant role in shaping differences among forests.
Early quantitative syntheses revealed that C fluxes such as net primary productivity ($NPP$) decrease dramatically with latitude, or increase across gradients of mean annual temperature and, to a lesser extent, precipitation [@lieth_primary_1973].

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap =TrB_age_trends_caption, out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/stacked_age_trends/Tropical broadleaf_age_trends.png")
```

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap =TeB_age_trends_caption, out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/stacked_age_trends/Temperate broadleaf_age_trends.png")
```

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap =TeN_age_trends_caption, out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/stacked_age_trends/Temperate conifer_age_trends.png")
```

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap =BoN_age_trends_caption, out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/stacked_age_trends/Boreal conifer_age_trends.png")
```
